### 2014-06-28 Choosing R3 Relations.tex
r3b_rln_fst_try_triangle

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}

@@

>>>>

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newcommand\tri{s_3^{-1}}
\newcommand\tr{s_3}
\newcommand\twi{s_2^{-1}}
\newcommand\tw{s_2}
\newcommand\oni{s_1^{-1}}
\newcommand\on{s_1}

@@

\section{Relations for 2,2,1 triangle, talk to Aaron if you think there's an error}

\begin{lem}
The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\twi\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

To show the first, equivalence, note
\begin{align*}
	s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 &=
\end{align*}

We only have to show the first two imply the third. We can use the first two identities to deduce $\tw\tri = \tri\on\tr\tw\tri\oni,\twi\tri=\tri\oni\tr\twi\tri\on.$ Indeed, we can see

\begin{align*}
	e &= \tw\tr\tw\tri\twi\tri
	\\
	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\tri\oni\tr\twi\tri\on)
	\\
	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\tri\oni\tr\twi\on\oni\tri\on)
	\\
	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= \tw\tr(\tri\on\tr\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= \tw\tr(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
\end{align*}

Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ NOTE: I FIGURED OUT HOW TO DO THIS BEFORE, BUT IM TOO TIRED NOW, AND I COULD HAVE MADE A MISTAKE, SO SOMEONE ELSE SHOULD CHECK, IF ITS WRONG THIS IS ALL WRONG.
This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\twi\tri\on\tr =e.$ Plugging this in yields
\begin{align*}
	e &= (\oni\tr\on\tr\on\tw\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on\oni\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
\end{align*}

So, since $e = \oni\tr\on\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on\oni\tri\on,$ cancelling three terms from both sides, we get $e =\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on,$ as claimed.
\end{proof}
